|

### 2020-04-03 Paper 2019.Rmd
Includes submitted JOPskeleton

---
title: | 
  | Campaign Contribution Limits and Corruption 
  | Evidence from the 50 states
author: "Mark Hand"
date: "01/06/2018"
output: pdf_document
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}
- \doublespacing
---

@@

```{r Barber summary, eval=T}
# This is a summary it, but includes all the 99999s and doesn't have skew in it. 
# stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)

>>>>

---
title: | 
  | Campaign Contribution Limits and Corruption 
  | Evidence from the 50 states
author: "Mark C. Hand"
date: "01/06/2018"
output: pdf_document
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}
- \doublespacing
---

@@

```{r Barber summary, eval=T}
# This is a summary, but includes all the 99999s and doesn't have skew in it. 
# stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)
